---
title: "Evaluating Monetary Policy Counterfactuals Caravello, McKay & Wolf (2026)"
subtitle: "Replication using R and C++"
author: "Mauricio Vargas Sepulveda"
format: 
  beamer:
    theme: "Madrid"
    colortheme: "dolphin"
    fonttheme: "structurebold"
    navigation: horizontal
    section-titles: true
    toc: false
    aspectratio: 169
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(ggplot2)
library(dplyr)
```

# Main Findings

## The Central Question

How do we evaluate monetary policy counterfactuals?

- Traditional approach: Build micro-founded DSGE model, change policy, re-solve
- Semi-structural approach: Directly leverage empirical evidence from historical policy variation

This paper bridges both traditions:

> Use as much reduced-form empirical evidence as possible, supplement with minimal structure necessary

---

## Key Result: Sufficient Statistics

To evaluate monetary policy counterfactuals, you only need two objects:

1. Policy Causal Effects $\Theta^\nu$
   - IRFs of all possible policy rate changes on macro outcomes
   - Effects across the entire yield curve (short-end to long-end)

2. Reduced-Form Projections
   - Wold impulse responses (average business cycle)
   - Forecasts (conditional historical counterfactuals)

$\implies$ You do not need the full structural model, shock processes, or the policy rule itself!

---

## What Empirical Evidence Tells Us

The constraint: Existing monetary policy shock literature primarily identifies effects of *transitory* rate changes (short end of yield curve)

- Romer-Romer (2004): Short-lived policy rate changes
- Aruoba-Drechsel (2024): Somewhat more persistent
- Gertler-Karadi (2015), Miranda-Agrippino-Ricco (2023): Similar

Missing piece: Causal effects of *delayed or persistent* rate changes

$\implies$ Need structural models to extrapolate beyond observed data variation

---

## The Extrapolation Question

Four structural models for extrapolation:

| Model  | Agents         | Expectations |
|--------|----------------|--------------|
| RANK   | Representative | Rational     |
| HANK   | Heterogeneous  | Rational     |
| B-RANK | Representative | Behavioural  |
| B-HANK | Heterogeneous  | Behavioural  |

Key finding: Once matched to short-end IRFs:

- RANK vs HANK $\implies$ similar extrapolation
- Behavioural frictions $\implies$ very different extrapolation

---

## Why HANK $\approx$ RANK (When Matched)

Intuition:

1. Market incompleteness can dampen or amplify monetary transmission
2. But: matching to *identical short-end effects* means heterogeneity channels largely offset
3. Result: "as-if" aggregation (echoes Werning, 2015)

Implication: For aggregate counterfactuals, whether we use RANK or HANK is largely immaterial

What matters: Strength of behavioural frictions (expectation formation)

# Methodology

## Bayesian VAR Estimation

Estimate reduced-form dynamics using BVAR with flat prior:

$$Y_t = B_1 Y_{t-1} + \cdots + B_p Y_{t-p} + u_t$$

Variables included:

- Unemployment, Output, Investment, Consumption
- Hours, TFP, Labor Productivity, Labor Share
- Inflation, Federal Funds Rate

Sample: 1960-1 to 2019-4, quarterly data

---

## Computing Wold IRFs

Wold representation: $y_t = \sum_{\ell=0}^{\infty} \Psi_\ell u_{t-\ell}$

Implementation:

1. Decompose $\Sigma = LL'$ (Cholesky)
2. Compute Wold coefficients recursively from companion form
3. Apply rotation: $\text{IRF}_h = \Theta_h \cdot L$

I was able to use R and **armadillo4r** to recreate the same figures as the article.

* $\implies$ advantage: free as in free of charge replication, open source and cross-platform independent validation
* $\implies$ disadvantage: not free in time, Armadillo requires some C++ knowledge (not as user-friendly as MATLAB)

See \url{https://github.com/pachadotdev/ecod024/tree/main/cmw26} for the replication code.

---

## Counterfactual Computation

Given policy rule $A_\pi \pi + A_y y + A_i i = \omega$:

Find optimal shock sequence:
$$\nu^* = -\left(M'M\right)^{-1} M' \cdot \text{target}$$

where $M = A_\pi \Pi_m + A_y Y_m + A_i I_m$

Counterfactual outcomes:
$$\tilde{\pi} = \pi + \Pi_m \nu^*, \quad \tilde{y} = y + Y_m \nu^*, \quad \tilde{i} = i + I_m \nu^*$$

---

## Optimal Policy Computation

Dual mandate loss function:

$$\mathcal{L} = \sum_{t=0}^T \beta^t \left[ \lambda_\pi \pi_t^2 + \lambda_y y_t^2 + \lambda_{\Delta i} (i_t - i_{t-1})^2 \right]$$

Solve for optimal policy path via quadratic programming:

$$\min_\nu \frac{1}{2}\nu' H \nu + f'\nu$$

# Results: Figures 3-5

```{r figure-3, fig.width=10, fig.height=5}
plot_list <- readRDS("./figure-3.rds")
plot_list[[2]]
```

---

```{r figure-3b, fig.width=10, fig.height=5}
plot_list[[1]]
```

---

```{r figure-4, fig.width=10, fig.height=5}
readRDS("./figure-4.rds")
```

---

```{r figure-5, fig.width=10, fig.height=5}
readRDS("./figure-5.rds")
```

# Table 5.1: Counterfactual Second Moments

```{r table-5-1}
knitr::kable(readRDS("./table-5-1.rds"))
```

---

```{r figure-d1, fig.width=10, fig.height=5}
readRDS("./figure-d1.rds")
```

# Figures 6-8

```{r figure-6, fig.width=10, fig.height=4}
readRDS("./figure-6.rds")
```

---

```{r figure-7-1, fig.width=10, fig.height=5}
f7 <- readRDS("./figure-7.rds")
f7[[1]]
```

---

```{r figure-7-2, fig.width=10, fig.height=5}
f7[[2]]
```

---

```{r figure-7-3, fig.width=10, fig.height=5}
f7[[3]]
```

---

```{r figure-8-1, fig.width=10, fig.height=4}
f8 <- readRDS("./figure-8.rds")
f8[[1]]
```

---

```{r figure-8-2, fig.width=10, fig.height=4}
f8[[2]]
```

---

```{r figure-8-3, fig.width=10, fig.height=4}
f8[[3]]
```

# Key Takeaways

## Summary of Findings

1. Semi-structural approach often suffices $\implies$ When counterfactual is about near-term policy, model extrapolation adds little
2. RANK $\approx$ HANK for aggregates $\implies$ Once matched to short-end IRFs, household heterogeneity doesn't matter much
3. Behavioral frictions are crucial
   - $\implies$ Forward guidance effectiveness depends critically on expectation formation
   - $\implies$ B-RANK/B-HANK predict much weaker effects of anticipated policy
4. Great Recession: Dual mandate central bank would have preferred deeply negative rate
5. Post-COVID: Standard models suggest forward guidance could stabilize inflation; behavioral models disagree

---

## Implications for Policy Analysis

Practical guidance for counterfactual evaluation:

- Check if contemplated policy changes are mainly about *near-term* rates
  - If yes $\implies$ semi-structural approach likely sufficient
  - If no $\implies$ need structural model for extrapolation

- For extrapolation, focus on:
  - Matching short-end policy effects (discipline the model)
  - Behavioral assumptions about expectations (key for long-end effects)
  - *Not* on RANK vs HANK distinction
