---
title: "Replicating CMW26: Evaluating Monetary Policy Counterfactuals"
subtitle: "R Port of Caravello, McKay & Wolf (2026)"
format: 
  html:
    toc: true
    toc-depth: 3
---

## Overview

This vignette replicates the main results from "Evaluating Monetary Policy 
Counterfactuals: (When) Do We Need Structural Models?" by Caravello, McKay, 
and Wolf (2026) using the R package `cmw26`.

The original MATLAB code (`main_mp_modelcnfctls.m`) produces:

- **Figure 2**: Monetary policy IRFs (Aruoba-Drechsel and Romer-Romer shocks)
- **Figures 3-4**: Matched model IRFs vs empirical VAR estimates
- **Figure 5**: News shock IRFs (anticipated monetary policy)
- **Table 5.1 & Figures D.1-D.2**: Counterfactual second moments
- **Figure 6**: Main business cycle shock counterfactuals
- **Figure 7**: Historical evolution (Great Recession)
- **Figure 8**: Historical scenario (post-COVID inflation)

This replication uses the R implementations in the `cmw26` package to perform
computations equivalent to the original MATLAB code.

## Setup

```{r setup}
#| message: false
#| warning: false

library(cmw26)
library(ggplot2)
library(dplyr)
library(tidyr)

# Paths - relative to workspace root
data_path <- "./cmw26-replication/var_inputs/_data/main"
suff_stats_path <- "./cmw26-replication/suff_stats"

# Display settings
theme_set(theme_minimal(base_size = 12))
```

## 1. Load and Prepare Data

### 1.1 Load Raw Data

The CMW data contains quarterly macroeconomic series from 1954Q3 onwards.

```{r load-raw-data}
# Load raw data (same data used by MATLAB code)
data_raw <- read.csv(file.path(data_path, "_data_cmw.csv"))
```

### 1.2 Transform Variables

Following the MATLAB code (`run_var_wold.m`), we transform the data:

- GDP, Investment, Consumption, Hours, TFP, Labor Productivity, Labor Share: 
  100 * Hamilton-filtered log levels
- Inflation: annualized rate (400 * quarterly change)
- Interest Rate: annualized Federal Funds Rate

```{r transform-data}
# Extract series
gdp <- data_raw$gdp
unemp <- data_raw$unemp
ffr <- 4 * data_raw$ffr  # Annualize
infl <- 100 * 4 * data_raw$infl  # Annualize
inv <- data_raw$inv
cons <- data_raw$cons
lab <- data_raw$lab
lab_share <- data_raw$lab_share
lab_prod <- data_raw$lab_prod
tfp <- data_raw$tfp

# Apply Hamilton filter (h=8, p=4) to level variables
# This removes low-frequency trends while preserving business cycle variation
gdp_hp <- 100 * hamilton(gdp, h = 8, p = 4)
inv_hp <- 100 * hamilton(inv, h = 8, p = 4)
cons_hp <- 100 * hamilton(cons, h = 8, p = 4)
lab_hp <- 100 * hamilton(lab, h = 8, p = 4)
lab_share_hp <- 100 * hamilton(lab_share, h = 8, p = 4)
lab_prod_hp <- 100 * hamilton(lab_prod, h = 8, p = 4)
tfp_hp <- 100 * hamilton(tfp, h = 8, p = 4)

# Combine into VAR data matrix
# Order: unemp, gdp, inv, cons, lab, tfp, lab_prod, lab_share, infl, ffr
vardata_full <- cbind(unemp, gdp_hp, inv_hp, cons_hp, lab_hp, tfp_hp, 
                       lab_prod_hp, lab_share_hp, infl, ffr)

series_names <- c("Unemployment", "Output", "Investment", "Consumption", 
                   "Hours", "TFP", "Labor Productivity", "Labor Share", 
                   "Inflation", "Interest Rate")
colnames(vardata_full) <- series_names

# Sample selection (1960Q1 to 2019Q4, matches MATLAB)
date <- data_raw$date
startdate <- which(date == 1960)
enddate <- which(date == 2019.75)

vardata <- vardata_full[startdate:enddate, ]

# Demean the data - MATLAB uses detrend() which removes LINEAR trend (not just mean)
# MATLAB's detrend removes best fit line y = a + b*t
# const_type = 2 matches MATLAB: remove constant AND linear trend
vardata_dt <- detrend(vardata, const_type = 2)$Res
colnames(vardata_dt) <- series_names  # Preserve column names
```

## 2. Load Sufficient Statistics

The sufficient statistics contain posterior draws of the monetary policy 
causal effect matrices from four structural models:

1. **RE RANK**: Rational Expectations Representative Agent New Keynesian
2. **RE HANK**: Rational Expectations Heterogeneous Agent New Keynesian
3. **Behav. RANK**: Behavioral RANK
4. **Behav. HANK**: Behavioral HANK

The key objects are:
- `Pi.m.collector`: Inflation response to monetary policy (T x T x n_draws)
- `Y.m.collector`: Output response to monetary policy  
- `R.n.m.collector`: Interest rate response to monetary policy

```{r load-suffstats}
# Load RE models
rank_draws <- readRDS(file.path(suff_stats_path, "ratex/rank_draws_main.rds"))
hank_draws <- readRDS(file.path(suff_stats_path, "ratex/hank_draws_main.rds"))

# Load behavioral models
brank_draws <- readRDS(file.path(suff_stats_path, "behavioral/rank_draws_main_behav.rds"))
bhank_draws <- readRDS(file.path(suff_stats_path, "behavioral/hank_draws_main_behav.rds"))

# Load all models mixture (draws sampled according to posterior model probabilities)
all_models <- readRDS(file.path(suff_stats_path, "mix/all_models_draws.rds"))

# Extract dimensions
T_model <- dim(rank_draws$Pi.m.collector)[1]
n_draws <- dim(rank_draws$Pi.m.collector)[3]

# Model posterior probabilities
if ("model.posteriors.all.models" %in% names(all_models)) {
  model_probs <- all_models$model.posteriors.all.models
}
```

## 3. Application Settings

```{r settings}
# Sample settings
indic_early <- FALSE   # TRUE: early sample (1960-2007), FALSE: standard (1960-2019)

# Model selection for counterfactuals
indic_models <- TRUE   # Report all four models separately?
indic_emp <- FALSE     # Use purely empirical approach?

# Counterfactual policy rule (select one)
cnfctl_rule <- "optpol"  # Options: "output_gap", "inflation", "rate_peg", 
                          #          "taylor", "ngdp", "optpol"
```

## 4. VAR Estimation and Wold IRFs

Following the MATLAB code (`run_var_wold.m`), we estimate a Bayesian VAR 
and compute Wold impulse response functions.

### 4.1 Estimate Bayesian VAR

```{r estimate-bvar}
# VAR settings (same as MATLAB run_var_wold.m)
n_lags <- 4           # Number of lags
constant <- 0         # No constant (data is detrended)
IRF_hor <- 250        # IRF horizon (MATLAB uses 250)
n_var_draws <- 1000   # Number of posterior draws

# Estimate BVAR with flat prior (essentially OLS)
bvar_result <- estimate_bvar(vardata_dt, n_lags = n_lags, 
                              constant = constant, n_draws = n_var_draws)
```

### 4.2 Compute Wold IRFs

The Wold decomposition provides orthogonalized impulse responses to 
structural shocks (using Cholesky rotation for identification).

```{r compute-wold}
n_y <- ncol(vardata_dt)

# Benchmark rotation (Cholesky decomposition)
bench_rot <- t(chol(bvar_result$Sigma_OLS))

# Compute Wold IRFs from OLS estimates
Theta_OLS <- array(0, dim = c(n_y, n_y, IRF_hor))
Theta_OLS[, , 1] <- diag(n_y)

# Companion form coefficients
B_mat <- bvar_result$B_OLS

for (l in 1:(IRF_hor - 1)) {
  for (j in 1:min(l, n_lags)) {
    B_j <- B_mat[((j - 1) * n_y + 1):(j * n_y), ]
    Theta_OLS[, , l + 1] <- Theta_OLS[, , l + 1] + t(B_j) %*% Theta_OLS[, , l - j + 1]
  }
}

# Apply rotation to get structural IRFs
IRF_OLS <- array(0, dim = c(n_y, n_y, IRF_hor))
for (h in 1:IRF_hor) {
  IRF_OLS[, , h] <- Theta_OLS[, , h] %*% bench_rot
}
```

### 4.3 Visualize Key IRFs

```{r plot-wold-irfs}
#| fig-width: 10
#| fig-height: 8

# Extract inflation, output, and interest rate responses
# Variable order: [1] Unemp, [2] Output, [3] Inv, [4] Cons, [5] Hours, 
#                [6] TFP, [7] Lab Prod, [8] Lab Share, [9] Inflation, [10] Rate
var_idx <- c(9, 2, 10)  # Inflation, Output, Interest Rate
var_labels <- c("Inflation", "Output Gap", "Interest Rate")

# Plot responses to monetary policy shock (shock to interest rate, column 10)
shock_idx <- 10
plot_hor <- 40

df_irf <- data.frame(
  horizon = rep(0:(plot_hor - 1), length(var_idx)),
  variable = rep(var_labels, each = plot_hor),
  response = c(IRF_OLS[var_idx[1], shock_idx, 1:plot_hor],
               IRF_OLS[var_idx[2], shock_idx, 1:plot_hor],
               IRF_OLS[var_idx[3], shock_idx, 1:plot_hor])
)
df_irf$variable <- factor(df_irf$variable, levels = var_labels)

ggplot(df_irf, aes(x = horizon, y = response)) +
  geom_line(color = "steelblue", linewidth = 1) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~variable, scales = "free_y", ncol = 1) +
  labs(
    title = "Wold IRFs to Monetary Policy Shock",
    subtitle = "Cholesky identification (interest rate ordered last)",
    x = "Quarters",
    y = "Response"
  ) +
  theme_minimal()
```

## 5. Figures 3-5: Model IRFs and News Shocks

This section replicates Figures 3-5, which compare the estimated structural 
model IRFs to monetary policy shocks with those from the VAR and examine 
"news shock" responses (anticipated monetary policy changes).

### 5.1 Load Model Mode Estimates

```{r load-model-modes}
# Load modal posterior estimates for each model
# These contain the matched IRFs to VAR empirical estimates

params_rank <- readRDS(file.path(suff_stats_path, "ratex/params_rank_mode.rds"))
params_hank <- readRDS(file.path(suff_stats_path, "ratex/params_hank_mode.rds"))
params_brank <- readRDS(file.path(suff_stats_path, "behavioral/params_rank_mode_behav.rds"))
params_bhank <- readRDS(file.path(suff_stats_path, "behavioral/params_hank_mode_behav.rds"))

# Extract model IRFs and matching weights
# Columns of m.fit: [1] Aruoba-Drechsel, [2] Romer-Romer

T_model_full <- nrow(params_rank$Pi.m.rank)
```

### 5.2 Compute Matched Model IRFs

```{r compute-matched-irfs}
# Pad m.fit to full dimension
pad_mfit <- function(m_fit, T_full) {
  n_shocks <- ncol(m_fit)
  m_padded <- matrix(0, T_full, n_shocks)
  m_padded[1:nrow(m_fit), ] <- m_fit
  m_padded
}

m_fit_rank <- pad_mfit(params_rank$m.fit.rank, T_model_full)
m_fit_hank <- pad_mfit(params_hank$m.fit.hank, T_model_full)
m_fit_brank <- pad_mfit(params_brank$m.fit.rank, T_model_full)
m_fit_bhank <- pad_mfit(params_bhank$m.fit.hank, T_model_full)

# Compute matched IRFs: Pi_m * m_fit gives IRF path for each shock type
# Matched IRFs for RANK
Pi_m_rank_match <- params_rank$Pi.m.rank %*% m_fit_rank
Y_m_rank_match <- params_rank$Y.m.rank %*% m_fit_rank
R_n_m_rank_match <- params_rank$R.n.m.rank %*% m_fit_rank

# Matched IRFs for HANK
Pi_m_hank_match <- params_hank$Pi.m.hank %*% m_fit_hank
Y_m_hank_match <- params_hank$Y.m.hank %*% m_fit_hank
R_n_m_hank_match <- params_hank$R.n.m.hank %*% m_fit_hank

# Matched IRFs for B-RANK
Pi_m_brank_match <- params_brank$Pi.m.rank %*% m_fit_brank
Y_m_brank_match <- params_brank$Y.m.rank %*% m_fit_brank
R_n_m_brank_match <- params_brank$R.n.m.rank %*% m_fit_brank

# Matched IRFs for B-HANK
Pi_m_bhank_match <- params_bhank$Pi.m.hank %*% m_fit_bhank
Y_m_bhank_match <- params_bhank$Y.m.hank %*% m_fit_bhank
R_n_m_bhank_match <- params_bhank$R.n.m.hank %*% m_fit_bhank
```

### 5.3 Figures 3-4: Model IRFs vs Empirical (AD and RR Shocks)

```{r compute-empirical-irfs-fig34}
# Compute empirical VAR IRFs for AD and RR shocks (same as MATLAB run_var_mp_adrr.m)
# This is done independently rather than loading MATLAB outputs

# Load data with shock series
data_emp_fig34 <- read.csv(file.path(data_path, "_data_cmw.csv"))

# Extract series
ad_shock_fig34 <- data_emp_fig34$ad
rr_shock_fig34 <- data_emp_fig34$rr_1

# Transform macro variables
gdp_emp_fig34 <- 100 * hamilton(data_emp_fig34$gdp, h = 8, p = 4)
infl_emp_fig34 <- 100 * 4 * data_emp_fig34$infl
ffr_emp_fig34 <- 4 * data_emp_fig34$ffr

# Sample: 1969-2006.75
date_emp_fig34 <- data_emp_fig34$date
startdate_emp_fig34 <- which(date_emp_fig34 == 1969)
enddate_emp_fig34 <- which(date_emp_fig34 == 2006.75)

# Build VAR data: [ad_shock, gdp, infl, rr_shock, ffr]
vardata_emp_fig34 <- cbind(ad_shock_fig34, gdp_emp_fig34, infl_emp_fig34, 
                            rr_shock_fig34, ffr_emp_fig34)
vardata_emp_fig34 <- vardata_emp_fig34[startdate_emp_fig34:enddate_emp_fig34, ]
vardata_emp_fig34[is.na(vardata_emp_fig34)] <- 0

# VAR settings (same as MATLAB)
n_lags_fig34 <- 2
constant_fig34 <- 2
IRF_hor_fig34 <- 200
n_draws_fig34 <- 1000
n_y_fig34 <- ncol(vardata_emp_fig34)

# Shock positions: AD at column 1, RR at column 4
shock_pos_fig34 <- c(1, 4)
n_shocks_fig34 <- length(shock_pos_fig34)

# Estimate BVAR
bvar_fig34 <- estimate_bvar(vardata_emp_fig34, n_lags = n_lags_fig34, 
                             constant = constant_fig34, n_draws = n_draws_fig34)

# Compute IRFs for OLS and each draw
irf_draws_fig34 <- array(NA, dim = c(IRF_hor_fig34, n_y_fig34, n_shocks_fig34, n_draws_fig34))

for (i_draw in seq_len(n_draws_fig34)) {
  Sigma_u <- bvar_fig34$Sigma_draws[[i_draw]]
  B <- bvar_fig34$B_draws[[i_draw]]
  bench_rot <- t(chol(Sigma_u))
  
  IRF_Wold <- array(0, dim = c(n_y_fig34, n_y_fig34, IRF_hor_fig34))
  IRF_Wold[, , 1] <- diag(n_y_fig34)
  
  for (l in 1:(IRF_hor_fig34 - 1)) {
    for (j in 1:min(l, n_lags_fig34)) {
      B_j <- B[((j - 1) * n_y_fig34 + 1):(j * n_y_fig34), ]
      IRF_Wold[, , l + 1] <- IRF_Wold[, , l + 1] + t(B_j) %*% IRF_Wold[, , l - j + 1]
    }
  }
  
  IRF_draw <- array(0, dim = c(n_y_fig34, n_y_fig34, IRF_hor_fig34))
  for (h in 1:IRF_hor_fig34) {
    IRF_draw[, , h] <- IRF_Wold[, , h] %*% bench_rot
  }
  
  for (i_shock in seq_along(shock_pos_fig34)) {
    irf_draws_fig34[, , i_shock, i_draw] <- t(IRF_draw[, shock_pos_fig34[i_shock], ])
  }
}

# Compute OLS IRFs
bench_rot_ols_fig34 <- t(chol(bvar_fig34$Sigma_OLS))
IRF_Wold_ols_fig34 <- array(0, dim = c(n_y_fig34, n_y_fig34, IRF_hor_fig34))
IRF_Wold_ols_fig34[, , 1] <- diag(n_y_fig34)

for (l in 1:(IRF_hor_fig34 - 1)) {
  for (j in 1:min(l, n_lags_fig34)) {
    B_j <- bvar_fig34$B_OLS[((j - 1) * n_y_fig34 + 1):(j * n_y_fig34), ]
    IRF_Wold_ols_fig34[, , l + 1] <- IRF_Wold_ols_fig34[, , l + 1] + 
      t(B_j) %*% IRF_Wold_ols_fig34[, , l - j + 1]
  }
}

IRF_ols_fig34 <- array(0, dim = c(n_y_fig34, n_y_fig34, IRF_hor_fig34))
for (h in 1:IRF_hor_fig34) {
  IRF_ols_fig34[, , h] <- IRF_Wold_ols_fig34[, , h] %*% bench_rot_ols_fig34
}

irf_ols_fig34 <- array(NA, dim = c(IRF_hor_fig34, n_y_fig34, n_shocks_fig34))
for (i_shock in seq_along(shock_pos_fig34)) {
  irf_ols_fig34[, , i_shock] <- t(IRF_ols_fig34[, shock_pos_fig34[i_shock], ])
}

# Extract empirical IRFs: Output (2), Inflation (3), Interest Rate (5)
# OLS median
Y_m_emp <- irf_ols_fig34[, 2, ]      # Output
Pi_m_emp <- irf_ols_fig34[, 3, ]     # Inflation  
R_n_m_emp <- irf_ols_fig34[, 5, ]    # Interest rate

# Confidence bands (16th and 84th percentiles)
Y_m_lb_emp <- apply(irf_draws_fig34[, 2, , ], c(1, 2), quantile, 0.16)
Y_m_ub_emp <- apply(irf_draws_fig34[, 2, , ], c(1, 2), quantile, 0.84)
Pi_m_lb_emp <- apply(irf_draws_fig34[, 3, , ], c(1, 2), quantile, 0.16)
Pi_m_ub_emp <- apply(irf_draws_fig34[, 3, , ], c(1, 2), quantile, 0.84)
R_n_m_lb_emp <- apply(irf_draws_fig34[, 5, , ], c(1, 2), quantile, 0.16)
R_n_m_ub_emp <- apply(irf_draws_fig34[, 5, , ], c(1, 2), quantile, 0.84)
```

```{r figures-3-4}
#| fig-width: 12
#| fig-height: 10

# Plot horizon
IRF_hor_plot <- 25

# Model colors
colors_models <- c("#C4AE78", "#CC0000")

shock_names <- c("Aruoba-Drechsel", "Romer-Romer")

# Create combined plot for both shocks
plot_list <- list()

for (i_shock in 1:2) {
  # Scale by max empirical interest rate response (same as MATLAB)
  # R_n_m_emp is already annualized from the VAR estimation
  scale_factor <- 1 / max(abs(R_n_m_emp[1:IRF_hor_plot, i_shock]))
  
  # Build data frame for model IRFs
  df_match <- data.frame(
    horizon = rep(0:(IRF_hor_plot - 1), 12),
    value = c(
      scale_factor * Y_m_rank_match[1:IRF_hor_plot, i_shock],
      scale_factor * Y_m_hank_match[1:IRF_hor_plot, i_shock],
      scale_factor * Y_m_brank_match[1:IRF_hor_plot, i_shock],
      scale_factor * Y_m_bhank_match[1:IRF_hor_plot, i_shock],
      scale_factor * 4 * Pi_m_rank_match[1:IRF_hor_plot, i_shock],
      scale_factor * 4 * Pi_m_hank_match[1:IRF_hor_plot, i_shock],
      scale_factor * 4 * Pi_m_brank_match[1:IRF_hor_plot, i_shock],
      scale_factor * 4 * Pi_m_bhank_match[1:IRF_hor_plot, i_shock],
      scale_factor * 4 * R_n_m_rank_match[1:IRF_hor_plot, i_shock],
      scale_factor * 4 * R_n_m_hank_match[1:IRF_hor_plot, i_shock],
      scale_factor * 4 * R_n_m_brank_match[1:IRF_hor_plot, i_shock],
      scale_factor * 4 * R_n_m_bhank_match[1:IRF_hor_plot, i_shock]
    ),
    model = rep(rep(c("RANK", "HANK", "B-RANK", "B-HANK"), each = IRF_hor_plot), 3),
    variable = rep(c("Output", "Inflation", "Interest Rate"), each = 4 * IRF_hor_plot)
  )
  
  # Add empirical IRFs with confidence bands
  df_emp <- data.frame(
    horizon = rep(0:(IRF_hor_plot - 1), 3),
    value = c(
      scale_factor * Y_m_emp[1:IRF_hor_plot, i_shock],
      scale_factor * Pi_m_emp[1:IRF_hor_plot, i_shock],
      scale_factor * R_n_m_emp[1:IRF_hor_plot, i_shock]
    ),
    lower = c(
      scale_factor * Y_m_lb_emp[1:IRF_hor_plot, i_shock],
      scale_factor * Pi_m_lb_emp[1:IRF_hor_plot, i_shock],
      scale_factor * R_n_m_lb_emp[1:IRF_hor_plot, i_shock]
    ),
    upper = c(
      scale_factor * Y_m_ub_emp[1:IRF_hor_plot, i_shock],
      scale_factor * Pi_m_ub_emp[1:IRF_hor_plot, i_shock],
      scale_factor * R_n_m_ub_emp[1:IRF_hor_plot, i_shock]
    ),
    variable = rep(c("Output", "Inflation", "Interest Rate"), each = IRF_hor_plot)
  )
  
  df_match$variable <- factor(df_match$variable, 
                               levels = c("Output", "Inflation", "Interest Rate"))
  df_match$model <- factor(df_match$model, 
                            levels = c("RANK", "HANK", "B-RANK", "B-HANK"))
  df_emp$variable <- factor(df_emp$variable,
                             levels = c("Output", "Inflation", "Interest Rate"))
  
  # Empirical color based on shock type (grey for AD, purple for RR)
  emp_color <- if (i_shock == 1) "#828282" else "#A020F0"
  emp_label <- if (i_shock == 1) "Empirical (AD)" else "Empirical (RR)"
  
  # Add model column to empirical data for legend
  df_emp$model <- emp_label
  
  p <- ggplot() +
    # Empirical bands
    geom_ribbon(data = df_emp, aes(x = horizon, ymin = lower, ymax = upper),
                fill = emp_color, alpha = 0.5) +
    # Empirical median (mapped to color for legend)
    geom_line(data = df_emp, aes(x = horizon, y = value, color = model),
              linewidth = 1.5) +
    # Model IRFs
    geom_line(data = df_match, aes(x = horizon, y = value, color = model, linetype = model),
              linewidth = 1) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    facet_wrap(~variable, scales = "free_y", ncol = 3) +
    scale_color_manual(
      values = c("RANK" = colors_models[1], "HANK" = colors_models[2],
                 "B-RANK" = colors_models[1], "B-HANK" = colors_models[2],
                 "Empirical (AD)" = "#828282", "Empirical (RR)" = "#A020F0"),
      breaks = c(emp_label, "RANK", "HANK", "B-RANK", "B-HANK")
    ) +
    scale_linetype_manual(
      values = c("RANK" = "solid", "HANK" = "solid",
                 "B-RANK" = "dashed", "B-HANK" = "dashed"),
      guide = "none"  # Hide linetype legend, use color only
    ) +
    labs(
      title = paste0("Figure 3-", i_shock, ": Model IRFs - ", shock_names[i_shock], " Shock"),
      subtitle = "Shaded band = Empirical VAR (68% CI)",
      x = "Quarters",
      y = "% Deviation (normalized)",
      color = "Model"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
  
  plot_list[[i_shock]] <- p
}

# Print plots (the article starts with Romer)
plot_list[[2]]
plot_list[[1]]
```

### 5.4 Figure 5: News Shock IRFs

A "news shock" is an anticipated monetary policy change. Here we examine 
the response to a monetary policy shock that is announced 16 quarters 
(4 years) in advance.

```{r figure-5-compute}
# News shock horizon (anticipated 16 quarters ahead)
news_horizon <- 16

# Create news shock vector: unit shock at horizon 16
m_news <- rep(0, T_model_full)
m_news[news_horizon] <- 1

# Compute news shock IRFs for each model using posterior draws
# This shows the response to policy that agents anticipate

n_draws_news <- min(100, n_draws)
IRF_hor_news <- 41

# Storage for news shock IRFs
news_irfs <- list()

for (model_name in c("rank", "hank", "brank", "bhank")) {
  if (model_name == "rank") {
    draws <- rank_draws
    Pi_name <- "Pi.m.collector"
    Y_name <- "Y.m.collector"
    R_name <- "R.n.m.collector"
  } else if (model_name == "hank") {
    draws <- hank_draws
    Pi_name <- "Pi.m.collector"
    Y_name <- "Y.m.collector"
    R_name <- "R.n.m.collector"
  } else if (model_name == "brank") {
    draws <- brank_draws
    Pi_name <- "Pi.m.collector"
    Y_name <- "Y.m.collector"
    R_name <- "R.n.m.collector"
  } else {
    draws <- bhank_draws
    Pi_name <- "Pi.m.collector"
    Y_name <- "Y.m.collector"
    R_name <- "R.n.m.collector"
  }
  
  T_draw <- dim(draws[[Pi_name]])[1]
  n_actual_draws <- min(n_draws_news, dim(draws[[Pi_name]])[3])
  
  # Extend m_news to match draw dimensions
  m_news_draw <- rep(0, T_draw)
  m_news_draw[news_horizon] <- 1
  
  Pi_news <- matrix(NA, IRF_hor_news, n_actual_draws)
  Y_news <- matrix(NA, IRF_hor_news, n_actual_draws)
  R_news <- matrix(NA, IRF_hor_news, n_actual_draws)
  
  for (d in seq_len(n_actual_draws)) {
    Pi_news[, d] <- (draws[[Pi_name]][1:IRF_hor_news, , d] %*% m_news_draw)[, 1]
    Y_news[, d] <- (draws[[Y_name]][1:IRF_hor_news, , d] %*% m_news_draw)[, 1]
    R_news[, d] <- (draws[[R_name]][1:IRF_hor_news, , d] %*% m_news_draw)[, 1]
  }
  
  news_irfs[[model_name]] <- list(
    Pi_med = apply(Pi_news, 1, median),
    Pi_lb = apply(Pi_news, 1, quantile, 0.16),
    Pi_ub = apply(Pi_news, 1, quantile, 0.84),
    Y_med = apply(Y_news, 1, median),
    Y_lb = apply(Y_news, 1, quantile, 0.16),
    Y_ub = apply(Y_news, 1, quantile, 0.84),
    R_med = apply(R_news, 1, median),
    R_lb = apply(R_news, 1, quantile, 0.16),
    R_ub = apply(R_news, 1, quantile, 0.84)
  )
}
```

```{r figure-5-plot}
#| fig-width: 12
#| fig-height: 5

# Figure 4: RANK vs HANK
df_news_rankhank <- data.frame(
  horizon = rep(0:(IRF_hor_news - 1), 6),
  value = c(
    news_irfs$rank$Y_med, news_irfs$hank$Y_med,
    4 * news_irfs$rank$Pi_med, 4 * news_irfs$hank$Pi_med,
    4 * news_irfs$rank$R_med, 4 * news_irfs$hank$R_med
  ),
  lower = c(
    news_irfs$rank$Y_lb, news_irfs$hank$Y_lb,
    4 * news_irfs$rank$Pi_lb, 4 * news_irfs$hank$Pi_lb,
    4 * news_irfs$rank$R_lb, 4 * news_irfs$hank$R_lb
  ),
  upper = c(
    news_irfs$rank$Y_ub, news_irfs$hank$Y_ub,
    4 * news_irfs$rank$Pi_ub, 4 * news_irfs$hank$Pi_ub,
    4 * news_irfs$rank$R_ub, 4 * news_irfs$hank$R_ub
  ),
  model = rep(rep(c("RANK", "HANK"), each = IRF_hor_news), 3),
  variable = rep(c("Output", "Inflation", "Interest Rate"), each = 2 * IRF_hor_news)
)

df_news_rankhank$variable <- factor(df_news_rankhank$variable,
                                     levels = c("Output", "Inflation", "Interest Rate"))

p4 <- ggplot(df_news_rankhank, aes(x = horizon, y = value, color = model, fill = model)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, color = NA) +
  geom_line(linewidth = 1) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_vline(xintercept = news_horizon, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~variable, scales = "free_y", ncol = 3) +
  scale_color_manual(values = c("RANK" = "#C4AE78", "HANK" = "#CC0000")) +
  scale_fill_manual(values = c("RANK" = "#C4AE78", "HANK" = "#CC0000")) +
  labs(
    title = "Figure 4: News Shock IRFs - RANK vs HANK",
    subtitle = paste0("Response to monetary policy shock anticipated ", news_horizon, 
                       " quarters ahead (68% bands)"),
    x = "Quarters",
    y = "% Deviation (annualized)",
    color = "Model",
    fill = "Model"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")

# Figure 5: RANK vs B-RANK
df_news_rankbrank <- data.frame(
  horizon = rep(0:(IRF_hor_news - 1), 6),
  value = c(
    news_irfs$rank$Y_med, news_irfs$brank$Y_med,
    4 * news_irfs$rank$Pi_med, 4 * news_irfs$brank$Pi_med,
    4 * news_irfs$rank$R_med, 4 * news_irfs$brank$R_med
  ),
  lower = c(
    news_irfs$rank$Y_lb, news_irfs$brank$Y_lb,
    4 * news_irfs$rank$Pi_lb, 4 * news_irfs$brank$Pi_lb,
    4 * news_irfs$rank$R_lb, 4 * news_irfs$brank$R_lb
  ),
  upper = c(
    news_irfs$rank$Y_ub, news_irfs$brank$Y_ub,
    4 * news_irfs$rank$Pi_ub, 4 * news_irfs$brank$Pi_ub,
    4 * news_irfs$rank$R_ub, 4 * news_irfs$brank$R_ub
  ),
  model = rep(rep(c("RANK", "B-RANK"), each = IRF_hor_news), 3),
  variable = rep(c("Output", "Inflation", "Interest Rate"), each = 2 * IRF_hor_news)
)

df_news_rankbrank$variable <- factor(df_news_rankbrank$variable,
                                      levels = c("Output", "Inflation", "Interest Rate"))

p5 <- ggplot(df_news_rankbrank, aes(x = horizon, y = value, color = model, fill = model)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, color = NA) +
  geom_line(linewidth = 1) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_vline(xintercept = news_horizon, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~variable, scales = "free_y", ncol = 3) +
  scale_color_manual(values = c("RANK" = "#C4AE78", "B-RANK" = "#66B2FF")) +
  scale_fill_manual(values = c("RANK" = "#C4AE78", "B-RANK" = "#66B2FF")) +
  labs(
    title = "Figure 5: News Shock IRFs - RANK vs B-RANK",
    subtitle = paste0("Response to monetary policy shock anticipated ", news_horizon, 
                       " quarters ahead (68% bands)"),
    x = "Quarters",
    y = "% Deviation (annualized)",
    color = "Model",
    fill = "Model"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")

p4
p5
```

## 6. Table 5.1: Counterfactual Second Moments

This section replicates Table 5.1 and Figure D.1, which show how business cycle 
statistics change under counterfactual policy rules.

### 6.1 Helper Function: Extract Policy IRFs

```{r helper-extract-irfs}
#' Extract policy IRF matrices from loaded RDS data
#' @param data RDS data loaded from MATLAB .mat file  
#' @param T_use Horizon to use (if NULL, uses full model dimension)
#' @return List with Pi_m, Y_m, I_m as lists of matrices
#' @details Following MATLAB code (import_suffstats.m):
#'   - Pi_m and I_m are scaled by 4 to annualize (quarterly to annual)
#'   - Y_m is NOT scaled
extract_model_irfs <- function(data, T_use = NULL) {
  # Data has Pi.m.collector, Y.m.collector, R.n.m.collector
  # Get full dimensions
  T_full <- dim(data$Pi.m.collector)[1]
  if (is.null(T_use)) T_use <- T_full
  
  # Extract and SCALE by 4 for Pi_m and I_m (annualize)
  # This matches MATLAB: Pi_m_draws = 4 * Pi_m_collector
  Pi_m_raw <- 4 * data$Pi.m.collector[1:T_use, 1:T_use, ]
  Y_m_raw <- data$Y.m.collector[1:T_use, 1:T_use, ]
  I_m_raw <- 4 * data$R.n.m.collector[1:T_use, 1:T_use, ]
  
  n_draws <- dim(Pi_m_raw)[3]
  
  list(
    Pi_m = lapply(seq_len(n_draws), function(i) Pi_m_raw[, , i]),
    Y_m = lapply(seq_len(n_draws), function(i) Y_m_raw[, , i]),
    I_m = lapply(seq_len(n_draws), function(i) I_m_raw[, , i]),
    n_draws = n_draws,
    T = T_use
  )
}
```

### 6.2 Prepare Baseline Wold IRFs

```{r prepare-wold-base}
# Extract IRFs from all models mixture first to get the model horizon T
# MATLAB: T = size(Pi_m_rank_draws, 1)
irfs_all <- extract_model_irfs(all_models, T_use = NULL)
T_hor <- irfs_all$T
n_shocks <- dim(IRF_OLS)[2]

# Extract relevant variables: inflation (9), output (2), interest rate (10)
# MATLAB: wold_base = IS_wold.Theta_OLS([9 2 10],:,1:T)
wold_base <- IRF_OLS[c(9, 2, 10), , 1:T_hor]
```

### 6.3 Baseline Business Cycle Statistics

```{r baseline-stats}
# Compute baseline VMA-implied covariance
cov_base <- matrix(0, 3, 3)
for (h in 1:T_hor) {
  Theta_h <- wold_base[, , h]
  cov_base <- cov_base + Theta_h %*% t(Theta_h)
}

# Standard deviations and correlations
std_base <- sqrt(diag(cov_base))
corr_base <- cov_to_corr_r(cov_base)

var_names_short <- c("Output", "Inflation", "Rate")
names(std_base) <- var_names_short
dimnames(corr_base) <- list(var_names_short, var_names_short)
```

### 6.4 Set Up Policy Rule

```{r setup-policy-rule}
# Set up optimal policy (dual mandate) weights
# Loss = sum_t beta^t * (lambda_pi * pi_t^2 + lambda_y * y_t^2 + lambda_di * (i_t - i_{t-1})^2)

weights <- set_optpol_weights(
  T = T_hor,
  lambda_pi = 1,    # Weight on inflation
  lambda_y = 1,     # Weight on output gap  
  lambda_i = 0,     # No penalty on interest rate level
  lambda_di = 1,    # Penalty on interest rate changes
  beta = 1          # Discount factor
)
```

### 6.5 Compute Counterfactual Wold IRFs for Each Model

```{r compute-counterfactual-models}
# Extract IRFs from each model separately (with proper 4x scaling for Pi_m and I_m)
irfs_rank <- extract_model_irfs(rank_draws, T_use = T_hor)
irfs_hank <- extract_model_irfs(hank_draws, T_use = T_hor)
irfs_brank <- extract_model_irfs(brank_draws, T_use = T_hor)
irfs_bhank <- extract_model_irfs(bhank_draws, T_use = T_hor)

model_names <- c("RANK", "HANK", "B-RANK", "B-HANK")
model_irfs_list <- list(irfs_rank, irfs_hank, irfs_brank, irfs_bhank)

n_draws_use <- min(1000, irfs_rank$n_draws)
n_models <- 4

# Storage for counterfactual COVARIANCES by model (not std devs)
# MATLAB: takes quantile of covariance FIRST, then sqrt
# Dimensions: (variable, variable, draw, model)
cov_cnfctl_models <- array(NA, dim = c(3, 3, n_draws_use, n_models))

for (m in seq_len(n_models)) {
  irfs_m <- model_irfs_list[[m]]
  
  for (d in seq_len(n_draws_use)) {
    Pi_m <- irfs_m$Pi_m[[d]]
    Y_m <- irfs_m$Y_m[[d]]
    I_m <- irfs_m$I_m[[d]]
    
    # Compute counterfactual Wold for all shocks
    wold_cnfctl_d <- array(0, dim = c(3, n_shocks, T_hor))
    
    for (s in seq_len(n_shocks)) {
      pi_z <- wold_base[1, s, ]
      y_z <- wold_base[2, s, ]
      i_z <- wold_base[3, s, ]
      
      result <- compute_optpol(pi_z, y_z, i_z, Pi_m, Y_m, I_m, weights)
      
      wold_cnfctl_d[1, s, ] <- result$pi_z_optpol
      wold_cnfctl_d[2, s, ] <- result$y_z_optpol
      wold_cnfctl_d[3, s, ] <- result$i_z_optpol
    }
    
    # Compute VMA covariance
    cov_d <- matrix(0, 3, 3)
    for (h in seq_len(T_hor)) {
      Theta_h <- wold_cnfctl_d[, , h]
      cov_d <- cov_d + Theta_h %*% t(Theta_h)
    }
    
    # Store full covariance (not just diagonal)
    cov_cnfctl_models[, , d, m] <- cov_d
  }
}
```

### 6.6 Load Empirical Sufficient Statistics (Semi-structural)

Following `import_suffstats_emp.m`, we load the pre-computed empirical monetary
policy IRFs from the MATLAB BVAR estimation. This ensures exact replication of
the MATLAB results by using the same posterior draws.

```{r load-empirical-suffstats}
# Load pre-computed MATLAB empirical IRF draws
# These were computed by run_var_mp_adrr.m and saved in IRFs_adrr_results.mat
# Converted to RDS format for R usage
emp_irfs <- readRDS(file.path(suff_stats_path, "empirical_irfs_adrr.rds"))

# MATLAB dimensions: (T x 1 x n_shocks x n_draws) = (200 x 1 x 2 x 1000)
# Following import_suffstats_emp.m:
# "No need to multiply or divide by 4 since empirical IRFs are all measured
#  in annualized terms."

# Extract and reshape draws to (T x n_shocks x n_draws)
Pi_m_emp_draws <- drop(emp_irfs$Pi.m.draws.emp)  # Inflation
Y_m_emp_draws <- drop(emp_irfs$Y.m.draws.emp)    # Output
I_m_emp_draws <- drop(emp_irfs$R.n.m.draws.emp)  # Interest Rate

# Get dimensions
T_emp_use <- dim(Pi_m_emp_draws)[1]
n_shocks_emp <- dim(Pi_m_emp_draws)[2]
n_draws_emp <- dim(Pi_m_emp_draws)[3]
```

```{r compute-semi-structural-counterfactuals}
# Compute counterfactual for empirical (semi-structural) approach
n_draws_emp_use <- min(1000, n_draws_emp)

# Verify dimension consistency before proceeding
# MATLAB requires model_T == empirical_T (both should be 200)
# If they differ, the code would fail with dimension mismatches
stopifnot("T_emp_use must equal T_hor for semi-structural to work. Check model sufficient statistics dimensions." = T_emp_use == T_hor)

# IMPORTANT: Following MATLAB exactly - use the SAME weights as model computation
# MATLAB does NOT create new weights for the empirical section; it reuses
# the weights created earlier with T = model_T
weights_emp <- weights

# Storage for empirical counterfactual COVARIANCES (not std devs)
# MATLAB: takes quantile of covariance FIRST, then sqrt
cov_cnfctl_emp <- array(NA, dim = c(3, 3, n_draws_emp_use))

for (d in seq_len(n_draws_emp_use)) {
  # Get empirical IRFs for this draw
  # Note: dimensions are (T x n_shocks) for each variable
  Pi_m <- Pi_m_emp_draws[, , d]
  Y_m <- Y_m_emp_draws[, , d]
  I_m <- I_m_emp_draws[, , d]
  
  # Compute counterfactual Wold for all original shocks
  # Use T_hor to match MATLAB (should equal T_emp_use = 200)
  wold_cnfctl_d <- array(0, dim = c(3, n_shocks, T_hor))
  
  for (s in seq_len(n_shocks)) {
    # MATLAB: pi_z = squeeze(wold_base(1,i_shock,:)) - uses ALL of wold_base
    # wold_base has shape (3, n_shocks, T_hor)
    pi_z <- wold_base[1, s, ]
    y_z <- wold_base[2, s, ]
    i_z <- wold_base[3, s, ]
    
    result <- compute_optpol(pi_z, y_z, i_z, Pi_m, Y_m, I_m, weights_emp)
    
    wold_cnfctl_d[1, s, ] <- result$pi_z_optpol
    wold_cnfctl_d[2, s, ] <- result$y_z_optpol
    wold_cnfctl_d[3, s, ] <- result$i_z_optpol
  }
  
  # Compute VMA covariance - sum over T_hor horizons (matching MATLAB)
  cov_d <- matrix(0, 3, 3)
  for (h in seq_len(T_hor)) {
    Theta_h <- wold_cnfctl_d[, , h]
    cov_d <- cov_d + Theta_h %*% t(Theta_h)
  }
  
  # Store full covariance (not just diagonal)
  cov_cnfctl_emp[, , d] <- cov_d  
}
```

### 6.7 Compute Summary Statistics

```{r counterfactual-stats}
# MATLAB approach: take quantiles of COVARIANCE, then sqrt of diagonal
# This differs from taking sqrt first then quantile (Jensen's inequality)

# Summary statistics for each model
std_model_summary <- list()

for (m in seq_len(n_models)) {
  # Extract covariance matrices for this model: (3, 3, n_draws)
  cov_m <- cov_cnfctl_models[, , , m]
  
  # Compute quantiles of covariance for each element
  cov_lb <- apply(cov_m, c(1, 2), quantile, probs = 0.16)
  cov_med <- apply(cov_m, c(1, 2), quantile, probs = 0.5)
  cov_ub <- apply(cov_m, c(1, 2), quantile, probs = 0.84)
  
  # Take sqrt of diagonal AFTER taking quantile (MATLAB approach)
  std_model_summary[[model_names[m]]] <- list(
    med = sqrt(diag(cov_med)),
    lb = sqrt(diag(cov_lb)),
    ub = sqrt(diag(cov_ub))
  )
}

# Summary for empirical (semi-structural)
# Compute quantiles of covariance for each element
cov_emp_lb <- apply(cov_cnfctl_emp, c(1, 2), quantile, probs = 0.16)
cov_emp_med <- apply(cov_cnfctl_emp, c(1, 2), quantile, probs = 0.5)
cov_emp_ub <- apply(cov_cnfctl_emp, c(1, 2), quantile, probs = 0.84)

# Take sqrt of diagonal AFTER taking quantile (MATLAB approach)
std_emp_summary <- list(
  med = sqrt(diag(cov_emp_med)),
  lb = sqrt(diag(cov_emp_lb)),
  ub = sqrt(diag(cov_emp_ub))
)
```

### 6.8 Table 5.1 Output

```{r table-5-1-output}
# Create Table 5.1 as a data frame

# Helper to format median with CI
fmt_ci <- function(med, lb, ub) {
 sprintf("%.3f (%.3f, %.3f)", med, lb, ub)
}

# Build rows for each model
table_rows <- list()

# Baseline (actual)
table_rows[[1]] <- data.frame(
  Approach = "Actual",
  Model = "",
  Inflation = sprintf("%.3f", std_base[1]),
  Output = sprintf("%.3f", std_base[2]),
  `Interest Rate` = sprintf("%.3f", std_base[3]),
  check.names = FALSE
)

# Hybrid models
for (m_name in model_names) {
  s <- std_model_summary[[m_name]]
  table_rows[[length(table_rows) + 1]] <- data.frame(
    Approach = "Hybrid",
    Model = m_name,
    Inflation = fmt_ci(s$med[1], s$lb[1], s$ub[1]),
    Output = fmt_ci(s$med[2], s$lb[2], s$ub[2]),
    `Interest Rate` = fmt_ci(s$med[3], s$lb[3], s$ub[3]),
    check.names = FALSE
  )
}

# Semi-structural
table_rows[[length(table_rows) + 1]] <- data.frame(
  Approach = "Semi-structural",
  Model = "",
  Inflation = fmt_ci(std_emp_summary$med[1], std_emp_summary$lb[1], std_emp_summary$ub[1]),
  Output = fmt_ci(std_emp_summary$med[2], std_emp_summary$lb[2], std_emp_summary$ub[2]),
  `Interest Rate` = fmt_ci(std_emp_summary$med[3], std_emp_summary$lb[3], std_emp_summary$ub[3]),
  check.names = FALSE
)

# Combine into single data frame
table_5_1 <- do.call(rbind, table_rows)
rownames(table_5_1) <- NULL

knitr::kable(table_5_1, 
             caption = "Table 5.1: Business Cycle Statistics Under Optimal Policy",
             align = c("l", "l", "r", "r", "r"))
```

Note: Posterior median with 16th and 84th percentiles in parentheses. Policy rule minimizes loss function with equal weight on inflation, output gap, and interest rate smoothing.

### 6.9 Visualize Distribution of Standard Deviations (Figure D.1)

```{r figure-d1}
#| fig-width: 12
#| fig-height: 6

# Compute std devs from covariance matrices for plotting
# For models: sqrt(diag(cov)) for each draw
std_cnfctl_models_plot <- array(NA, dim = c(3, n_draws_use, n_models))
for (m in seq_len(n_models)) {
  for (d in seq_len(n_draws_use)) {
    std_cnfctl_models_plot[, d, m] <- sqrt(diag(cov_cnfctl_models[, , d, m]))
  }
}

# Prepare data for plotting - only RANK model for kernel density (blue)
# Variable order in wold_base: [1]=Inflation, [2]=Output, [3]=Rate
# But var_names_short is ["Output", "Inflation", "Rate"] for display
# Need to reorder: Output=row2, Inflation=row1, Rate=row3
df_rank_density <- data.frame(
  variable = rep(var_names_short, each = n_draws_use),
  std_cnfctl = c(std_cnfctl_models_plot[2, , 1],  # Output (row 2)
                 std_cnfctl_models_plot[1, , 1],  # Inflation (row 1)
                 std_cnfctl_models_plot[3, , 1])  # Rate (row 3)
)
df_rank_density$variable <- factor(df_rank_density$variable, levels = var_names_short)

# Use std_model_summary which correctly computes sqrt(median(cov))
# MATLAB: sqrt(cnfctl_models.cov_med(i_y,i_y,i_model))
# Reorder to match var_names_short: [Output, Inflation, Rate]
# std_model_summary has order [Inflation, Output, Rate] from wold_base
mode_rank <- std_model_summary[["RANK"]]$med[c(2, 1, 3)]    # RANK
mode_hank <- std_model_summary[["HANK"]]$med[c(2, 1, 3)]    # HANK
mode_brank <- std_model_summary[["B-RANK"]]$med[c(2, 1, 3)] # B-RANK
mode_bhank <- std_model_summary[["B-HANK"]]$med[c(2, 1, 3)] # B-HANK

# Create data frame for vertical lines (posterior medians)
# MATLAB order: i_model 1=RANK, 2=HANK, 3=B-RANK, 4=B-HANK
df_modes <- data.frame(
  variable = factor(rep(var_names_short, 4), levels = var_names_short),
  mode_val = c(mode_rank, mode_hank, mode_brank, mode_bhank),
  model_type = rep(c("RANK", "HANK", "B-RANK", "B-HANK"), each = 3)
)

# Baseline values (black dashed)
# std_base has order [Inflation, Output, Rate], reorder to [Output, Inflation, Rate]
df_base <- data.frame(
  variable = factor(var_names_short, levels = var_names_short),
  std_base = std_base[c(2, 1, 3)]
)

ggplot() +
  # Blue kernel density for baseline RANK
  geom_density(data = df_rank_density, aes(x = std_cnfctl), 
               fill = "#4A90D9", color = "#4A90D9", alpha = 0.4) +
  # Black dashed: baseline (actual data)
  geom_vline(data = df_base, aes(xintercept = std_base), 
             color = "black", linetype = "dashed", linewidth = 1) +
  # Beige: RANK models posterior modes
  geom_vline(data = df_modes[df_modes$model_type == "RANK", ], 
             aes(xintercept = mode_val), color = "#C4AE78", linewidth = 1) +
  geom_vline(data = df_modes[df_modes$model_type == "B-RANK", ], 
             aes(xintercept = mode_val), color = "#C4AE78", linewidth = 1, linetype = "dotted") +
  # Red: HANK models posterior modes
  geom_vline(data = df_modes[df_modes$model_type == "HANK", ], 
             aes(xintercept = mode_val), color = "#CC0000", linewidth = 1) +
  geom_vline(data = df_modes[df_modes$model_type == "B-HANK", ], 
             aes(xintercept = mode_val), color = "#CC0000", linewidth = 1, linetype = "dotted") +
  facet_wrap(~variable, scales = "free", ncol = 3) +
  labs(
    title = "Figure D.1: Counterfactual Unconditional Volatilities",
    subtitle = "Black dashed = observed policy; Blue density = RANK posterior; Beige = RANK modes; Red = HANK modes",
    x = "Standard Deviation",
    y = "Density"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```
